WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-08-14 ms.tex
In-preparation reference for Sathya and Chu

Although the response time of \ac{BAYESTAR} has been driven by the anticipated timescales for kilonova and afterglow emission, a recurring question is whether there is any detectable \ac{EM} signal in the seconds before, during, and after the merger itself. An obvious example would be prompt gamma\nobreakdashes-ray emission, though more exotic ...

Since the \ac{GW} inspiral signal is in principal detectable for up to hundreds of seconds before merger, one could imagine positioning rapidly slewing instruments to search for prompt emission ...

@@

>>>>

@@

Although the response time of \ac{BAYESTAR} has been driven by the anticipated timescales for kilonova and afterglow emission, a recurring question is whether there is any detectable \ac{EM} signal in the seconds before, during, and after the merger itself. Since the \ac{GW} inspiral signal is in principal detectable for up to hundreds of seconds before merger, one could imagine positioning rapidly slewing instruments to search for any prompt emission. This concept was explored by the authors \citep{Cannon:2011vi}, and will be revisted in further detail in both Sathyaprakash et al. (in preparation) and Chu et al. (in preparation).
